Summary of the things that I learned

### 2024-10-14 910-alternative-definitions.tex
Slightly clean up chapter 4

This definition is more general than the definition of algebraic theory in Section \ref{sec:algebraic-theories}. To make it equivalent, we have to be more specific about the objects of the category:
\begin{definition}
  A \iindex{Lawvere theory}, or \textit{one-sorted algebraic theory} is a category $ L $, with $ L_0 = \{ 0, 1, \dots \} $, such that $ n = 1^n $, the $ n $-fold product.
\end{definition}

>>>>

This definition is more general than the definition of algebraic theory in Section \ref{sec:algebraic-theories}. To make it equivalent, we have to be more specific about the objects of the category:
\begin{definition}\label{def:lawvere-theory}
  A \iindex{Lawvere theory}, or \textit{one-sorted algebraic theory} is a category $ L $, with $ L_0 = \{ 0, 1, \dots \} $, such that $ n = 1^n $, the $ n $-fold product.
\end{definition}
